Learning Programs through Bayesian Inference and Planning

### 2013-10-23 drafts/nips/nips2013.tex
Edited abstract.

\begin{abstract}
How can machine learning techniques be used to solve problems whose solutions are best represented as computer programs? For example, suppose a researcher wants to design a probabilistic graphical model for a novel domain. On the one hand, designing a good model requires a great deal of domain-specific knowledge and expertise, which may be hard to come by. On the other hand, searching the space of probabilistic models automatically is notoriously difficult. However, when researchers do set out to design graphical models, they draw on abstractions such as trees, chains, grids and plates to constrain and direct the kinds of models they produce. Thus, if we want to produce machine learning tools that aid in this task, we want tools that can learn these kinds of relevant abstractions. One natural way to think of these abstractions is as programs that take sets of random variables and produce graphical models that relate them. In this work, we describe the SEC algorithm, which attempts to learn distributions over such programs by incrementally finding program components that commonly help solve problems in a given domain. We discuss the behavior of the SEC algorithm for the task of graphical model structure learning. We also describe SEC's behavior on the dissimilar problem of automatically constructing tall and physically stable towers of blocks. 
\end{abstract}

>>>>

\begin{abstract}
How can machine learning techniques be used to solve problems whose solutions are best represented as computer programs? For example, suppose a researcher wants to design a probabilistic graphical model for a novel domain. Searching the space of probabilistic models automatically is notoriously difficult and is especially difficult when the latent variables are possible. However, when researchers seem able to relatively easily adapt commonly used modeling motifs to new domains. In doing so, they draw on abstractions such as trees, chains, grids and plates to constrain and direct the kinds of models they produce. This suggests that before we ask machine learning algorithms to discover parsimonious models of new domains, we should develop techniques that enable our algorithms to automatically learn these ``graphical conepts'' in much the same way that researchers themselves do, by seeing examples in the literature. One natural way to think of these graphical concepts is as programs that take sets of random variables and produce graphical models that relate them. In this work, we describe the SEC algorithm, which attempts to learn a distribution over programs by incrementally finding program components that commonly help to solve problems in a given domain, and we show prelimarily that SEC is able to discover the graphical concepts that underlie many of the common graphical model structures.  
\end{abstract}
